Verifying Demonstrations

### 2018-11-09 paper/protest-model.tex
Fixes Douglas' comments for the protest model

\begin{definition}[Subprotest, Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in 
    \ZZ_{2^\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of 
  the cause of the protest,
  \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location (the topological connectedness is not necessary).
  A \emph{protest} is the set of subprotests sharing the same \(\cid\).
\end{definition}

@@

@@

% proof
% proofs
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  A \emph{participation proof} of a protester with pseudonym \(\pid\) who 
  participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
  set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, time 
  interval \(t\) and location \(l\) within those of the protest (\ie any 
  subprotest).
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

>>>>

\begin{definition}[Subprotest, Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in 
    \bin^{\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of 
  the cause of the protest,
  \(t \subseteq \TT\) is a time period and \(l \subseteq \LL\) is the location 
  (the topological connectedness is not necessary).
  A \emph{protest} is the set of subprotests sharing the same \(\cid\).
\end{definition}

@@

We will use the following notation to filter out a subset of \(\pshs\) with 
specific \(\cid\)s and \(\pid\)s:
\begin{multline*}
  \pshs_{\cid_0, \pid_0} = \\
  \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = \cid_0 \land \pid = \pid_0\}.
\end{multline*}

@@

% proof
% proofs
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  A \emph{participation proof} of a protester with pseudonym \(\pid\) who 
  participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
  set
  \begin{equation}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh \in \pshs_{\cid, \pid} \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\},
  \end{equation}
  of all proof shares with the same protester and protest identifiers, time 
  interval \(t\) and location \(l\) within those of the protest (\ie any 
  subprotest).
  We denote by \(\prfs\) the set of all proofs.
\end{definition}
